\bfseries A simple, anisotropic ram-pressure model for sailing

### 2021-06-21 paper/main.tex
include the first figure
Updates from Overleaf

\documentclass{article}
\usepackage[utf8]{inputenc}

% math macros
\usepackage{amsmath, amsfonts}
\DeclareMathOperator*{\argmax}{argmax}
\newcommand{\dd}{\mathrm{d}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\uvec}{\vec{\hat{e}}}
\newcommand{\tensor}[1]{\mathbb{#1}}
\renewcommand{\flat}{\text{flat}}
\newcommand{\iso}{\text{iso}}
\newcommand{\air}{\text{air}}
\newcommand{\water}{\text{water}}
\newcommand{\boat}{\text{boat}}
\newcommand{\destination}{\text{dest}}
\newcommand{\good}{\text{(good)}}
\newcommand{\better}{\text{(best)}}
\newcommand{\sail}{\text{sail}}
\newcommand{\keel}{\text{keel}}
\newcommand{\hull}{\text{hull}}
\renewcommand{\above}{\text{above}}
\newcommand{\below}{\text{below}}
\newcommand{\vair}{\vec{v}_\air}
\newcommand{\vwater}{\vec{v}_\water}
\newcommand{\vboat}{\vec{v}_\boat}
\newcommand{\vdest}{\vec{v}_\destination}

@@

% typesetting adjustments
\makeatletter
\renewcommand\section{\@startsection {section}{1}{\z@}%
  {-3.25ex \@plus -1ex \@minus -.2ex}%
  {1.5ex \@plus .2ex}%
  {\raggedright\normalfont\large\bfseries}}
\makeatother
\setlength{\textwidth}{5.00in}
\setlength{\textheight}{9.00in}
\setlength{\topmargin}{-0.40in}
\pagestyle{myheadings}
\markright{\textsf{Hogg \& Kleban / Ram-pressure model for sailing}}
\linespread{1.08}
\frenchspacing\sloppy\sloppypar\raggedbottom

@@

In \figref{fig:steady} we show examples of steady sailing, for a wide range of orientations of the keel and sail.
All these examples are shown in the water rest frame.
The boat has four free parameters $(A_\sail,A_\keel,A_{\above},A_{\below})$ all with units of area (or really three independent dimensionless ratios of these four areas).
The values we chose for these four parameters are given in \secref{sec:design} and discussed in detail there.
\begin{figure}[tp]
  \caption{Visualizations of the boat velocity $\vboat$ for different settings of the orientations of the keel and sail, all presented in the water rest frame.
    The views are top-down; the keel is represented by a thick grey line, the sail is represented by a thin black line, and the wind and boat velocities are represented by black arrows.
    Most of the settings of the keel and sail lead to downwind travel, but a few lead to upwind travel, for example XXX and YYY. HOGG LABEL THE PANELS.\label{fig:steady}}
\end{figure}

In \figref{fig:hourglass} we show the distribution of boat velocities one obtains if one randomly orients one's sail and keel....HOGG
HOGG: Put the random-dot hourglass figure here.

@@

A type-A sailor---or maybe a competetive sailor---is trying to get from a current position to a destination as quickly as possible\footnote{%
We don't particularly endorse this attitude towards sailing. The journey \emph{is} the destination.}.
Our view is that this sailor should start by specifying the unit vector $\uvec_\destination$ that points from the current position of the boat towards the destination of the boat.
The sailor should then maximize the scalar product $\uvec_\destination^\top\,\vboat$
\begin{align}\label{eq:better}
    \uvec_{\perp\sail}^\better,\uvec_{\perp\keel}^\better &\leftarrow \argmax_{\uvec_{\perp\sail},\uvec_{\perp\keel}} \left[\uvec_\destination^\top\,(\vboat-\vdest)\right] ~,
\end{align}
where $\uvec_{\perp\sail}^\better,\uvec_{\perp\keel}^\better$ are the best settings of the orientations of the keel and sail, given the direction $\uvec_\destination$ to the destination, and (because we are Galilean-relativistic) this velocity is relative to the velocity $\vdest$ of the destination (which might not be stationary with respect to the water).
In this expresion \eqref{eq:better}, implicitly $\vboat$ is being thought of as a function of these orientations (and more).
Note that the sailor \emph{does not necessarily want} to travel directly towards the destination:
The sailor wants to make as much progress as possible in that direction, but is willing to tack back-and-forth to get there, if it gets the boat there faster.
So the metric really is the projection of the boat velocity onto the displacement vector pointing from the current position of the boat to the destination.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{./}{../ipynb/}}

% math macros
\usepackage{amsmath, amsfonts}
\DeclareMathOperator*{\argmax}{argmax}
\newcommand{\dd}{\mathrm{d}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\uvec}{\vec{\hat{e}}}
\newcommand{\tensor}[1]{\mathbb{#1}}
\renewcommand{\flat}{\text{flat}}
\newcommand{\iso}{\text{iso}}
\newcommand{\air}{\text{air}}
\newcommand{\water}{\text{water}}
\newcommand{\boat}{\text{boat}}
\newcommand{\destination}{\text{dest}}
\newcommand{\good}{\text{(good)}}
\newcommand{\better}{\text{(better)}}
\newcommand{\sail}{\text{sail}}
\newcommand{\keel}{\text{keel}}
\newcommand{\hull}{\text{hull}}
\renewcommand{\above}{\text{above}}
\newcommand{\below}{\text{below}}
\newcommand{\vair}{\vec{v}_\air}
\newcommand{\vwater}{\vec{v}_\water}
\newcommand{\vboat}{\vec{v}_\boat}
\newcommand{\vdest}{\vec{v}_\destination}

@@

% typesetting adjustments
\makeatletter
\renewcommand\section{\@startsection {section}{1}{\z@}%
  {-3.25ex \@plus -1ex \@minus -.2ex}%
  {1.5ex \@plus .2ex}%
  {\raggedright\normalfont\large\bfseries}}
\makeatother
\setlength{\textwidth}{5.00in}
\setlength{\textheight}{9.00in}
\setlength{\topmargin}{-0.40in}
\pagestyle{myheadings}
\markright{\textsf{Hogg \& Kleban / Ram-pressure model for sailing}}
\newcommand{\figurerule}{\rule[1ex]{\textwidth}{0.2pt}}
\linespread{1.08}
\frenchspacing\sloppy\sloppypar\raggedbottom

@@

In \figref{fig:steady} we show examples of steady sailing, for a wide range of orientations of the keel and sail.
All these examples are shown in the water rest frame.
The boat has four free parameters $(A_\sail,A_\keel,A_{\above},A_{\below})$ all with units of area (or really three independent dimensionless ratios of these four areas).
The values we chose for these four parameters are given in \secref{sec:design} and discussed in detail there.
\begin{figure}[t!]
  \includegraphics[width=\textwidth]{steady.pdf}
  \caption{Visualizations of the boat velocity $\vboat$ for different settings of the orientations of the keel and sail, all presented in the water rest frame.
  The views are top-down; the keel is represented by a thick grey line, the sail is represented by a thin black line, and the wind and boat velocities are represented by black arrows.
  Most of the settings of the keel and sail lead to downwind travel, but a few in the top-left quarter of this grid lead to upwind travel.\label{fig:steady}}
  \figurerule
\end{figure}

In \figref{fig:hourglass} we show the distribution of boat velocities one obtains if one randomly orients one's sail and keel....HOGG
\begin{figure}[t!]
  \includegraphics[width=\textwidth]{hourglass-random.pdf}
  \caption{HOGG CAPTION HERE.\label{fig:hourglass}}
  \figurerule
\end{figure}

HOGG: Put the random-dot hourglass figure here.

@@

A type-A sailor---or maybe a competetive sailor---is trying to get from a current position to a destination as quickly as possible\footnote{%
We don't particularly endorse this attitude towards sailing. The journey \emph{is} the destination.}.
Our view is that this sailor should start by specifying the unit vector $\uvec_\destination$ that points from the current position of the boat towards the destination of the boat.
The sailor should then maximize the scalar product $\uvec_\destination^\top\,\vboat$
\begin{align}\label{eq:better}
    \uvec_{\perp\sail}^\better,\uvec_{\perp\keel}^\better &\leftarrow \argmax_{\uvec_{\perp\sail},\uvec_{\perp\keel}} \left[\uvec_\destination^\top\,(\vboat-\vdest)\right] ~,
\end{align}
where $\uvec_{\perp\sail}^\better,\uvec_{\perp\keel}^\better$ are the best settings of the orientations of the keel and sail, given the direction $\uvec_\destination$ to the destination, and (because we are Galilean-relativistic) this velocity is relative to the velocity $\vdest$ of the destination (which might not be stationary with respect to the water; imagine that we are sailing on a fast-flowing river).
In this expression \eqref{eq:better}, implicitly $\vboat$ is being thought of as a function of the orientations (and more).
Note that the sailor \emph{does not necessarily want} to travel directly towards the destination:
The sailor wants to make as much progress as possible in that direction, but is willing to tack back-and-forth to get there, if it gets the boat there faster.
So the metric really is the projection of the boat velocity onto the displacement vector pointing from the current position of the boat to the destination.
